Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-17 paper/paper.tex
fix(paper): Trailing whitespace
fix(paper): Fix meaning of FHS in Nix

@@

We were able to package nearly all components and run nearly all test cases showing the potential of Nix in the domain of scientific software. Many packages required workarounds, however, which might be difficult to achieve for none-experienced Nix users. 
Nix also comes with a few peculiarities, which complicate workarounds.
In fact, every piece of software has to lie within \texttt{/nix/store} and each path therein is its own-isolated tree based on the Filesystem Hierarchy Standard (FHS).

>>>>

% \begin{sloppypar}
% \end{sloppypar}

@@

We were able to package nearly all components and run nearly all test cases showing the potential of Nix in the domain of scientific software. Many packages required workarounds, however, which might be difficult to achieve for none-experienced Nix users.
Nix also comes with a few peculiarities, which complicate workarounds.
In fact, every piece of software has to lie within \texttt{/nix/store} and each path therein is its own-isolated tree inspired by the Filesystem Hierarchy Standard (FHS).
